\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{adjustbox}
\geometry{verbose,lmargin=2cm,rmargin=2cm,bmargin=2.5cm,tmargin=2cm}

\usepackage{booktabs}
\usepackage{natbib}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}



\newcommand{\rootdir}{..}  % one dir up
\newcommand{\plots}{\rootdir/output/plots}
\newcommand{\tables}{\rootdir/output/tables}


%% TITLE PAGE
\begin{document}
\onehalfspacing
    
    
\title{A Reproducible Benchmark of Fixed Effects Estimation}



\author{Florian Oswald\thanks{RES Data Editor. You can find the source code generating the entire workshop at \url{https://github.com/floswald/ReproData.jl}}}
\date{\today}


\maketitle
\begin{abstract}
We illustrate a workflow which tries to address several pitfalls when creating a reproducible research project. We focus on preserving raw data, documenting data sources, creating a folder structure, writing stata and R code in a way which helps to preserve the package version environment, outputting results to disk and referencing them in a final output document. As a by-product, we report timings of a typical two-way fixed effects estimation exercise on a large dataset.    
\end{abstract}

\section{Introduction}

One could be forgiven to think that reproducibility is as simple as following a few simple steps:

\begin{enumerate}
\item Preserve raw data
\item Document data origin
\item Preserve code and document how to use it
\item Run everything again before submitting the package.
\end{enumerate}

While this is a good start, this list if far from exhaustive, and a more complete version is available under \url{https://datacodestandard.org}. Whatever the list, however, the devil is in the details, and \emph{in practice} achieving reproducibility is far from trivial. We want to use this fictitious research project to illustrate one potential strategy when setting up code, and data, and a few associated pitfalls. 

\section{Computational Task}

In this paper, we want to estimate the following linear regression with two fixed effects:

\begin{equation}
y_{ij} = \beta X_{ij} + \alpha_i + \gamma_j + u_{ij} \label{eq:1}
\end{equation}
where $X_{ij}$ is a matrix which stacks the 1 by 7 vectors $[ x_{ij1}, \dots, x_{ij7}]$. The indices $(i,j)$ group observations along two ad-hoc dimensions: imagine person and time, or worker and firm specific effects. Those $\alpha_i,\gamma_j$ are unobservable.

We generated the data such that the first $x$ is a function of both fixed effects, $x_{it1} = g(\alpha_i, \gamma_t)$, the second a function only of $\gamma_t$, $x_{it2} = h(\gamma_t)$, and we set the true values for coefficients to $\beta = [ 3,3,1,1,1,1,1]$. Now let me show you the first result in table \ref{tab:1}. Observe that models (1) and (2) exhibit bias, and only after we account for both fixed effects, we get the correct results. Overall this seems to work.\footnote{The interested reader may consult the data generating process \href{https://github.com/floswald/ReproData.jl/blob/main/src/ReproData.jl}{here}.}

\begin{table}
\centering
\input{\tables/statareg.tex}
\caption{This is done with stata. I couldn't figure out why the FE2 row does not display a "yes" in columns 3 and 4. My bad, sorry!\label{tab:1}}
\end{table}
\end{document}
